Generating Simulated Data

### 2021-04-30 docs/SimData.Rmd
WIP stomach weight inputs

#requires function below
catchlen_ss <- read_savedfisheries(d.name, "catchLen")

@@

@@

>>>>

#requires read_savedfisheries function below, add to atlantisom
catchlen_ss <- read_savedfisheries(d.name, "catchLen")

@@

What we have saved so far is a diet comp in proportion that has had bias and observation error added to proportions. However, we need the stomach weight portion of the equation, which has the survey timing/area/efficiency/selectivity applied to true consumed weight.

@@

# apply surveys to true total consumption (snipped from atlantosom om_diet.R and om_comps.R)
detaileddiet <- readRDS(file.path(d.name, paste0(scenario.name, "detaileddiet.rds")))

usersurvey <- c(here("simulated-data/config/mssurvey_spring.R"),
                here("simulated-data/config/mssurvey_fall.R"),
                here("simulated-data/config/mssurvey_spring_01.R"),
                here("simulated-data/config/mssurvey_fall_01.R"))

survObsStomWt <- list()

for (s in usersurvey)
{
  source(s, local = TRUE)

  # survtime doesn't match units of time.days in detaileddiet
  survtime <- survey_sample_full*omlist_ss$runpar$outputstep

  # apply survey design to detailed diet
  survey_cons <- create_survey_diet(dat = detaileddiet,
                                    time = survtime,
                                    species = survspp,
                                    boxes = survboxes,
                                    effic = surveffic,
                                    selex = survselex)

  # get numbers at ageclass for same survey design
  survey_N <- atlantisom::create_survey(dat = omlist_ss$truenums_ss,
                                        time = survtime,
                                        species = survspp,
                                        boxes = survboxes,
                                        effic = surveffic,
                                        selex = survselex.agecl)

  # divide surv_cons by survey numbers at agecl to get per capita consumption at agecl

  #save survey consumption, takes a long time to generate with lots of reps/species
  #if(save){
  saveRDS(survey_cons, file.path(d.name, paste0(scenario.name, "_",
                                                survey.name, "surveycons.rds")))
  #}

  survObsStomWt[[survey.name]] <- survey_cons

# divide by survey numbers at agecl to get per capita consumption at agecl

# map to length bins using surey numbers at agecl in length bins

# #multiple surveys named in list object, use as filename
# for(s in names(all_diets)){
#   #arrange into wide format: year, Species1, Species2 ... and write csv
#   svdiet <- all_diets[[s]][[1]] %>%
#     #calc_timestep2time(d.name, ., run.prm.file) %>% #this gives an arbitrary start year of 1970
#     dplyr::mutate(time = time.days/NOBAom_ms$runpar$toutinc) %>%
#     dplyr::left_join(., trueBagecl) %>%
#     dplyr::mutate(dietBwt = dietSamp*trueBatage) %>%
#     dplyr::group_by(species,time,prey,trueB) %>%
#     dplyr::summarise(totdietBwt = sum(dietBwt)) %>%
#     dplyr::mutate(totdietComp = totdietBwt/trueB) %>%
#     dplyr::mutate(year = ceiling(time/stepperyr)) %>%
#     dplyr::ungroup() %>%
#     dplyr::select(year, species, prey, totdietComp) %>%
#     write_csv(paste0(o.name,"diet_",s,".csv"))
# }

We also plan to fit to time series of prey proportions for each predator size class. Gavin suggests an input format similar to those for survey lengths.

```{r preyatsize, eval=FALSE}

# same file as for MSSPM, diet proportion by agecl
all_diets <- read_savedsurvs(d.name, 'survDiet')

#
